Title here

### 2016-09-14 portfolio/text/ms.Rmd
Add to methods

- overview

- describe predictors

- We adjusted for inflation by setting all revenues in 2009 USD 
based on data from TODO.

We calculated effective species diversity for
permit holder $i$ and year $t$ as the inverse of 
Simpson's diversity index $\lambda$ [@simpson1949]
weighted by revenue $R$ (herein 'species diversity'):

@@

\noindent
where $s$ indexes species from $1$ through $n$.

>>>>

- overview
- describe predictors
- We adjusted for inflation by setting all revenues in 2009 USD 
based on data from TODO.
- note the filtering and referred to the supplement

## Predictors

Our models focused on the predictor species diversity, 
while controlling for effort. We calculated effective species diversity for
permit holder $i$ and year $t$ as the inverse of 
Simpson's diversity index $\lambda$ [@simpson1949]
weighted by revenue $R$ (herein 'species diversity'):

@@

\noindent
where $s$ indexes species from $1$ through $n$.
We calculated effort or effective season length as
the sum of days fished across each permit each year. 
For example, if someone fished for 30 days
on a salmon drift gillnet permit in Southeast Alaska
and 40 days on a statewide longline halibut permit,
that individual's season length 
would be 70 days.

## Hierarchical model
